### 2016-09-15 paper/2_overview.tex
Shorten gilbert features section

The resulting AST is attributed with type information by the typing system.
The typer makes use of the Hindley-Milner algorithm to automatically infer types, as it is described in \cref{sec:hmInference}.
The type information enriched AST is then translated into a front end independent representation of linear algebra operations, namely the IR.
The format Gilbert uses to represent linear algebra operations in a generalized format is described in \cref{cha:intermediaterepresentation}.

>>>>

The resulting AST is attributed with type information by the typing system.
The typer makes use of the Hindley-Milner algorithm to automatically infer types, as it is described in~\cref{sec:hmInference}.
The type information enriched AST is then translated into a front end independent representation of linear algebra operations, namely the IR.
The format Gilbert uses to represent linear algebra operations in a generalized format is described in \cref{sec:intermediaterepresentation}.
